Near and Mid-infrared properties of known $z\geq5$ Quasars

### 2019-05-28 tex/older_tex/VHzQ_20180527.tex
tex/older_tex/VHzQ_20180527.tex

Tables~\ref{tab:THE_TABLE}, \ref{tab:THE_TABLE_NIR} and~\ref{tab:THE_TABLE_MIR}, represent the culmination of this effort, and we now describe the assembly of their contents in more detail.

\input{table_tex/THE_TABLE_v0pnt96_TOP10_betterformat}

@@

      \begin{tabular}{l r l}
        \hline  \hline
        Selection   & number detected (\%) \\
        \hline  
        Any band ($ZYJHK/K_{s}$   &  394  (92.9) \\
        $Z$-band    &  72  (17.0) \\
        $Y$-band    &  249  (58.7) \\
        $J$-band    &  391  (92.2) \\
        $H$-band    &  258  (60.8) \\
        $K$ or $Ks$-band    &  297  ( ) \\
        \hline  \hline
      \end{tabular}
      \caption{Detection rate of VH$z$Qs in the near-infrared.}
      \label{tab:nir_detection}
    \end{table}

     There are 17 objects that have no NIR detections. 
     2 of these (PSOJ053.9605-15.7956 and PSO J056.7168-16.4769) 
     have been observed, but are out of our queried time range. 
     10 objects have not been observed (or at least the data is not in the WSA/VSA 
     archives yet) and 5 objects at $\geq +60$ deg$^{2}$ are too far north for UKIRT 
     and cannot be observed.

        \subsubsection{Comparing WFCAM and VISTA}
        There are 114 overlapping QSOs between WFCAM and VISTA.  Using the
        {\tt VegaToAB} value\footnote{What is this exactly??} to put these
        objects on the same AB system, and for each object compared the two
        measurements. First, the calculated weighted average (calibrated flux)
        in each filter of both and calculated the ratio and difference between
        each measurement and the average.  Then for each filter we calculated
        the weighted average of the differences (in mag) for each instrument
        to see if there were significant offsets. The results are given in
        Table~\ref{tab:WFCAM_vs_VISTA}.  The only filter with a significant
        offset is the $Y$-band. All of the VISTA averages are negative and all
        of the WFCAM ones are positive.  The $Ks$ versus $K$ band may be
        slightly dodgy, given the different shapes of the filters.
        \begin{table}
          \centering
          \begin{tabular}{l r r}
            \hline  \hline
            abs(VIRCAM & \multirow{2}{*}{millimags} &  no. of  \\
            -  WFCAM)      &                                        &  objects \\
            \hline
            $Z$                 &  19.3 	& 2 \\
            $Y$                 &  66.2 	& 48 \\
            $J$                  &    3.2 	& 105 \\
            $H$                 &  19.3     &  89 \\
            $K_{\rm s}$/$K$ &  12.7     & 93 \\
            \hline  \hline
          \end{tabular}
          \caption{Comparing the magnitudes in different WFCAM/UKIRT and VIRCAM/VISTA near-infrared bands.}
          \label{tab:WFCAM_vs_VISTA}
        \end{table}

>>>>

Tables~\ref{tab:WSA_wWISE}, \ref{tab:THE_TABLE_NIR} and~\ref{tab:THE_TABLE_MIR}, represent the culmination of this effort, and we now describe the assembly of their contents in more detail.

%\input{table_tex/WSA_wWISE}

%\input{table_tex/THE_TABLE_v0pnt96_TOP10_betterformat}

\input{../tables_for_paper/output_table}

@@

      \begin{tabular}{l r l}
        \hline  \hline
        Selection   & number detected (\%) \\
        \hline  
        Any band ($ZYJHK/K_{s}$   &  449  (97.0) \\
        $Z$-band    &  75  (16.1) \\
        $Y$-band    &  273  (59.0) \\
        $J$-band    &  447  (96.5) \\
        $H$-band    &  269  (58.1) \\
        $K$ or $Ks$-band    &  322  (69.5) \\
        \hline  \hline
      \end{tabular}
      \caption{Detection rate of VH$z$Qs in the near-infrared.}
      \label{tab:nir_detection}
    \end{table}

     There are 14 objects that have no NIR detections. 
     3 of these (PSOJ053.9605-15.7956, PSO J056.7168-16.4769 and DELSJ0411-0907) 
     have been observed (by VHS) but are out of our queried time range. 
     6 objects have not been observed (or at least the data is not in the WSA/VSA 
     archives yet) and 5 objects at $\geq +60$ deg$^{2}$ are too far north for UKIRT 
     and cannot be observed.

        \subsubsection{Comparing WFCAM and VISTA}
        There are 130 overlapping QSOs between WFCAM and VISTA.  Using the
        {\tt VegaToAB} value\footnote{What is this exactly??} to put these
        objects on the same AB system, and for each object compared the two
        measurements. First, the calculated weighted average (calibrated flux)
        in each filter of both and calculated the ratio and difference between
        each measurement and the average.  Then for each filter we calculated
        the weighted average of the differences (in mag) for each instrument
        to see if there were significant offsets. The results are given in
        Table~\ref{tab:WFCAM_vs_VISTA}.  The only filter with a significant
        offset is the $Y$-band. All of the VISTA averages are negative and all
        of the WFCAM ones are positive.  The $Ks$ versus $K$ band may be
        slightly dodgy, given the different shapes of the filters.
        \begin{table}
          \centering
          \begin{tabular}{l r r}
            \hline  \hline
            abs(VIRCAM & \multirow{2}{*}{millimags} &  no. of  \\
            -  WFCAM)      &                                        &  objects \\
            \hline
            $Z$                 &  23.2 	& 3 \\
            $Y$                 &  57.3 	& 53 \\
            $J$                  &    2.1 	& 106 \\
            $H$                 &  45.8     &  96 \\
            $K_{\rm s}$/$K$ &  25.2     & 110 \\
            \hline  \hline
          \end{tabular}
          \caption{Comparing the magnitudes in different WFCAM/UKIRT and VIRCAM/VISTA near-infrared bands.}
          \label{tab:WFCAM_vs_VISTA}
        \end{table}

        We investigate the VH$z$Qs in the UltraVISTA field. 
        UltraVISTA is...
        %% 
        One detail to note is that depths quoted in the UltraVISTA Data Releases are for more realistic 
        1.8 arcsec diameter apertures (J. Dunlop, priv. comm.).
